### 2015-03-20 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
Equipment: minor edit to guide

\headerC{
\flushright{
Kristopher J. Overholt \\
Craig G. Weinschenk \\
Roy A. McLane \\
Jay A. McElroy \\
Daniel Madrzykowski \\
\bigskip
{\em Fire Research Division \\
Engineering Laboratory \\
Gaithersburg, Maryland, USA} \\ }
}

@@

\begin{table}[h!]
\centering
\captionof{table}{Thermocouple Uncertainty}\label{tab:TC_uncertain}
\begin{tabular}{lll}
\toprule[1.5pt]
Thermocouple Type  &  Temperature Range     &  Error                                      \\
\midrule
Bare bead (SLE)    &  0 - 1250 $^{\circ}$C  &  MAX($\pm$ 1.1$^{\circ}$C; $\pm$ 0.4 $\%$)  \\
Inconel sheathed   &  0 - 1260 $^{\circ}$C  &  MAX($\pm$ 1.1$^{\circ}$C; $\pm$ 0.4 $\%$)  \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

>>>>

\headerC{
\flushright{
Kristopher J. Overholt \\
Craig G. Weinschenk \\
Keith M. Stakes \\
Roy A. McLane \\
Jay A. McElroy \\
Daniel Madrzykowski \\
\bigskip
{\em Fire Research Division \\
Engineering Laboratory \\
Gaithersburg, Maryland, USA} \\ }
}

@@

% \begin{table}[h!]
% \centering
% \captionof{table}{Thermocouple Uncertainty}\label{tab:TC_uncertain}
% \begin{tabular}{lll}
% \toprule[1.5pt]
% Thermocouple Type  &  Temperature Range     &  Error                                      \\
% \midrule
% Bare bead (SLE)    &  0 - 1250 $^{\circ}$C  &  MAX($\pm$ 1.1$^{\circ}$C; $\pm$ 0.4 $\%$)  \\
% Inconel sheathed   &  0 - 1260 $^{\circ}$C  &  MAX($\pm$ 1.1$^{\circ}$C; $\pm$ 0.4 $\%$)  \\
% \bottomrule[1.25pt]
% \end{tabular}\par
% \end{table}
